### 2022-11-11 NSF2022/Description/backgroundv2.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\todo[inline]{Bryan left off here}
\label{sec:bie}
\begin{wrapfigure}[10]{r}{2in}
  \todo[inline]{A figure comparing FEM versus BIE meshes}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  requires meshing the entire domain (typically into triangles), while a
  BIE only requires meshing the boundary of the domain.}
\end{wrapfigure}
The solution of PDEs in a domain surrounding a mobile, dense suspension
of bodies is highly nontrivial and requires accurate,
dimension-reducting discretization
that do not require continual remeshing.  
Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
including the Stokes equation~\eqref{eqn:stokes} and the phase
equation~\eqref{eqn:phase} in the special case of $f(u) =
\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
can be written as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega_t \rightarrow \RR^2$
is an unknown density function. The BIE reformulation has several
immediate advantages including a dimension reduction since $\ssigma$ is
defined only on $\partial \Omega_t$, and the far field boundary
condition of the PDE is automatically satisfied. The density
function $\ssigma$ is chosen to satisfy the boundary condition, and this
results in a BIE 
\begin{align*}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega_t,
\end{align*}
where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
constant that depends on the choice of $G$. For numerical stability,
choices of $G$ that result in second-kind Fredholm integral equations,
meaning $\lambda \neq 0$, are preferred.

A consequence of the dimension reduction in a BIE formulation is that
complex geometries are much easier to resolve than a mesh-based method
since only $\partial \Omega_t$ needs to be discretized
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
formulation includes a discretization that is high-order, or even
spectrally, accurate; results in a well-conditioned linear system that
can be solved iteratively with a mesh-independent number of iterations
of a Krylov method such as the generalized minimal residual method
(GMRES). However, BIEs do have several challenges: nearly touching
granules requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. The BIE community, including PI Quaife, has
developed a variety of tools to address these numerical challenges, and
we discuss our planned approach in Section~\ref{sec:specificaim2}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\todo[inline]{Bryan left off here}
\label{sec:bie}
The solution of PDEs in a domain surrounding a mobile, dense suspension
of bodies is highly nontrivial and requires accurate,
dimension-reducting discretization
that do not require continual remeshing.  
Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
including the Stokes equation~\eqref{eqn:stokes} and the phase
equation~\eqref{eqn:phase} in the special case of $f(u) =
\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
can be written as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
is an unknown density function. The BIE reformulation has several
immediate advantages including a dimension reduction since $\ssigma$ is
defined only on $\partial \Omega(t)$, and the far field boundary
condition of the PDE is automatically satisfied. The density
function $\ssigma$ is chosen to satisfy the boundary condition, and this
results in a BIE 
\begin{align*}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega(t),
\end{align*}
where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
constant that depends on the choice of $G$. For numerical stability,
choices of $G$ that result in second-kind Fredholm integral equations,
meaning $\lambda \neq 0$, are preferred.

\begin{wrapfigure}[]{l}{2.1in}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

A consequence of the dimension reduction in a BIE formulation is that
complex geometries are much easier to resolve than a mesh-based method
since only $\partial \Omega(t)$ needs to be discretized
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
formulation includes a discretization that is high-order, or even
spectrally, accurate; results in a well-conditioned linear system that
can be solved iteratively with a mesh-independent number of iterations
of a Krylov method such as the generalized minimal residual method
(GMRES). However, BIEs do have several challenges: nearly touching
granules requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. The BIE community, including PI Quaife, has
developed a variety of tools to address these numerical challenges, and
we discuss our planned approach in Section~\ref{sec:specificaim2}.
